---
output: 
  github_document:
    pandoc_args: --webtex=https://ibm.codecogs.com/png.latex?
always_allow_html: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  fig.path = "man/figures/README-",
  message = FALSE,
  #out.width = "100%",
  fig.width = 5,
  fig.height = 5
)
```

# ETAD: Election Timing across Autocracy and Democracy

## Overview

The ETAD dataset provides information of the dates when national elections were scheduled and held. 
It currently covers national legislative and presidential the periods between 1945 and 2023 for 148 countries.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("yukiyanai/ETAD")
```

or

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("yukiyanai/ETAD")
```

## Citation

When using the ETAD dataset, please remember to cite the following paper.

- Higashijima, Masaaki, Naoki Shimizu, Hidekuni Washida, and Yuki Yanai. (2025). "[Election Timing across Autocracy and Democracy (ETAD): A New Dataset of National Election Dates](https://doi.org/10.1016/j.electstud.2025.102964)." *Electoral Studies* 96, 102964.

## Data

You only have to load the **ETAD** package to use the data.
```{r}
library(ETAD)
```

Then, you can use the data object called `ETAD`. For instance, you can glance at the top rows of the dataset by:
```{r}
head(ETAD)
```

If you would like to use the dataset outside R, please export the dataset to a file as follows.

To export it to a CSV file:
```{r, eval=FALSE}
export_ETAD_csv(file = "fileNameOfYourChoice.csv")
```

To export it to a TSV file:
```{r, eval=FALSE}
export_ETAD_tsv(file = "fileNameOfYourChoice.tsv")
```


To export it to a file in Stata 14 dta format (you need **haven** package for this):
```{r, eval = FALSE}
export_ETAD_dta(file = "fileNameOfYourChoice.dta",
                version = 14)
```

## Codebook

[Codebook for ETAD (v.1)](https://yukiyanai.github.io/data_etad/ETAD_codebook_ver_1.pdf) (PDF)

## Authors

- [Masaaki Higashijima](https://masaakihigashijima.com/) (The University of Tokyo)
- Naoki Shimizu (Chukyo University)
- [Hidekuni Washida](https://orcid.org/0000-0003-2119-8127) (Toyo University)
- [Yuki Yanai](http://yukiyanai.github.io/) (Kochi University of Technology) [maintainer]
